---
title: "Portfolio Tables Report"
author: "CASE - Blaine Harper"
output:
  html_document:
    code_folding: hide
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Portfolio.R")
```

# IDS Tables {.tabset .tabset-fade .tabset-pills}

Interdisciplinary Studies

## Faculty County by Major

```{r IDS.FCbM}
IDS_Kables$Faculty.Count.by.Major
```

## Inter-rater Reliability

```{r IDS.IrR}
IDS_Kables$Inter.rater.Reliability
```

## Yearly Scores by Prefix

```{r IDS.YSbB}
IDS_Kables$Yearly.Scores.by.Prefix
```

## Mean Score by Major

```{r IDS.MSbM}
IDS_Kables$Mean.Scores.by.Major
```

# CTW Tables {.tabset .tabset-fade .tabset-pills}

Critical Thinking and Writing

## First Major 
```{r CTW.First.Major}
CTW_Kables$First.Major
```


## Scores by Final Major

```{r CTW.Final.Major}
CTW_Kables$Final.Major
```

## Scores by Course Prefix

```{r CTW.Final.Prefix}
CTW_Kables$Final.Prefix
```

## Inter-rater Reliability

```{r CTW.Inter.rater.Reliability}
CTW_Kables$Inter.rater.Reliability
```

## Faculty Score

```{r CTW.Faculty.Score}
CTW_Kables$Faculty.Score
```

## Course Prefix Score
```{r CTW.Course.Prefix.Score}
CTW_Kables$Course.Prefix.Score
```

# LTT {.tabset .tabset-fade .tabset-pills}
Letter to Truman

## Hours Spent
```{r LTT.Hours.Spent}
LTT_Kables$Hours.Spent
```

## Attitude towards Portfolio
```{r LTT.Attitude.Portfolio}
LTT_Kables$Attitude.Portfolio
```

## Attitude towards Education
```{r LTT.Attitude.Education}
LTT_Kables$Attitude.Education
```

## Self Reflection
```{r LTT.Self.Reflection}
LTT_Kables$Self.Reflection
```

# MOST {.tabset .tabset-fade .tabset-pills}

## Reasons
```{r MOST.Reasons}
MOST_Kables$Reasons
```

## Scores by First Major
```{r MOST.Scores.by.first.major}
MOST_Kables$Scores.by.first.major
```

# SELF {.tabset .tabset-fade .tabset-pills}

## Rationales
```{r SELF.Rationales}
SELF_Kables$Rationales
```

## SR, G, C Rationales
```{r SELF.SRGC_Rationales}
SELF_Kables$SRGC_Rationales
```

## A & S Rationales
```{r SELF.AS_Rationales}
SELF_Kables$AS_Rationales
```

## Relationship Rationales
```{r SELF.Rel_Rationales}
SELF_Kables$Rel_Rationales
```

# TEQ {.tabset .tabset-fade .tabset-pills}

## Overall Ed Transformative
```{r TEQ.Overall.Ed.Transformative}
TEQ_Kables$Overall.Ed.Transformative
```

## Various Activities
```{r TEQ.Various.Activities}
TEQ_Kables$Various.Activities
```

## Reporting Activity
```{r TEQ.Reporting.Activity}
TEQ_Kables$Reporting.Activity
```

## Activities by Gender
```{r TEQ.Activities.by.Gender}
TEQ_Kables$Activities.by.Gender
```

## Activities by Major
```{r TEQ.Activities.by.Major}
TEQ_Kables$Activities.by.Major
```

## Activities by Major - Percent Only
```{r TEQ.Activities.by.Major.percentOnly}
TEQ_Kables$Activities.by.Major.percentOnly
```

## Activities by Major Historically
```{r TEQ.Activity.Major.Over.Time}
TEQ_Kables$Activity.Major.Over.Time
```

## Majors by Gender
```{r TEQ.Majors.by.Gender}
TEQ_Kables$Majors.by.Gender
```

## Overall
```{r TEQ.Overall}
TEQ_Kables$Overall
```

## Overall (2015-2019)
```{r TEQ.Overall.Historical}
TEQ_Kables$Overall.Historical
```

